A boundary integral equation approach to computing eigenvalues of the Stokes operator

### 2019-03-29 doc/draft-01-stokes/04numerical.tex
add early changes to numerical section

>>>>

In order to turn the BIEs analyzed
above into discrete linear systems,
we require some standard techniques
from the BIE literature.

Let the boundary be divided into $N_p$
panels.
%
We parameterize panel $j$ as
$\bx_j(t)$, with $t$ ranging over the
interval $[-1,1]$.
%
Each component of $\bx_j$ is taken to be
a polynomial interpolant over the
standard 16th order Legendre nodes on
$[-1,1]$, denoted by $t_n$, so that
the total number of discretization
points is $N=16N_p$.
%
See \cref{fig:panels} for an example
discretization.
%
Another important quantity below is the
arc-length density of a panel, which
we denote by $s_j(t) := |\bx'_j(t)|$.
%
Finally, we denote the set of panels
which are adjacent to panel $i$
by $A(i)$. On a closed curve,
$A(i)$ contains two integers.

The integral kernels of the single and
double layer potentials have weak
singularities of the form $r^p\log r$
which require special quadrature rules to
achieve high-order accuracy.
%
In the examples below, we use generalized
Gaussian quadrature (GGQ)~\cite{bremer2010}.
%
To demonstrate the idea, we consider
evaluating the convolution of a kernel
$K$ with a density $\sigma$
at the boundary node $\xx_j(t_l)$.
%
GGQ is a Nystr\"{o}m-type discretization ---
the density is approximated 
by its values at the discretization nodes,
which we denote by
$\sigma_{qp} \approx \sigma(\xx_q(t_p))$.
%
The basis of a GGQ is a set of 
support nodes and weights for the
contribution to the integral from the
``self'' panel (panel $j$) and the adjacent
panels (with index in $A(j)$).
%

For the self panel, there is a special set
of nodes and weights for each interpolation
point. Denote the nodes and weights
for interpolation point $l$ by $t^{(l)}_{n}$
and $w^{(l)}_{n}$, respectively, with
$1\leq l \leq 16$ and $1\leq n \leq N_s$.
%
The adjacent panels are handled by a single
set of over-sampled support nodes and weights.
We denote these nodes and weights
by $\tilde{t}_n$ and $\tilde{w}_n$, respectively,
for $1 \leq n \leq N_a$.
%
For the rules we used, $N_s = 16$ and
$N_a = 48$.
%
The contribution of other panels is assumed
to be given to high accuracy by the standard
Gauss-Legendre weights, which we denote
by $w_n$.
%
Adding these contributions together, we obtain the
quadrature

\begin{multline}
  \int_\Gamma K(\xx_i(t_l),\yy) \, \sigma(\yy)
  \, dS(\yy) \approx \\
  \sum_{p=1}^{16} \sum_{n=1}^{N_s}
  w^{(l)}_{n} K(\xx_i(t_l),\xx_i({t}^{(l)}_{n}))
  s_i({t}^{(l)}_{n}) B^{(l)}_{np} \sigma_{ip} \quad \textrm{(self)}
  \\
  + \sum_{q\in A(i)} \sum_{p=1}^{16} \sum_{n=1}^{N_a}
  \tilde{w}_jK(\xx_i(t_l),\xx_q(\tilde{t}_n)) s_q(\tilde{t}_n)
  C_{np} \sigma_{qp}
  \quad \textrm{(adjacent)} \\
  + \sum_{q\neq i, q\not\in A(i)} \sum_{p=1}^{16}
  w_p K(\xx_i(t_l),\xx_q(t_p)) s_q(t_p)
  \sigma_{qp} \quad \textrm{(far)} \nonumber \; ,
\end{multline}
where $\bB^{(l)}$ and $\bC$ are interpolation
matrices from the standard Legendre nodes
to the self and adjacent panel support nodes,
respectively. Observe that the quadrature is
linear in $\sigma_{qp}$. In practice, we pre-compute
and store the self and adjacent matrix entries for each
interpolation point, which is a parallelizable
$O(N)$ calculation. The ``far'' interactions
are computed on-the-fly.

\subsection{Spurious eigenvalues --- annulus}
\label{subsec:spurannulus}

\subsection{Convergence study --- annulus}
\label{subsec:convannulus}

\subsection{Robustness on a nearly multiply connected domain}
\label{subsec:crescent}

\subsection{Eigenvalues of a domain with several inclusions}

### 2019-03-29 doc/draft-01-stokes/stokes-eig.tex
add early changes to numerical section

\def\bz{{\boldsymbol 0}}
\def\br{{\boldsymbol r}}
\def\bc{{\boldsymbol c}}
\def\bh{{\boldsymbol h}}
\def\bn{{\boldsymbol n}}
\def\bT{{\boldsymbol T}}
\def\bt{{\boldsymbol t}}
\def\xx{{\boldsymbol x}}
\def\bx{{\boldsymbol x}}
\def\yy{{\boldsymbol y}}
\def\by{{\boldsymbol y}}
\def\ss{{\boldsymbol s}}
\def\tt{{\boldsymbol t}}
\def\uu{{\boldsymbol u}}
\def\bu{{\boldsymbol u}}
\def\be{{\boldsymbol e}}
\def\bl{{\boldsymbol \ell}}
\def\ff{{\boldsymbol f}}
\def\bg{{\boldsymbol g}}
\def\GG{{\bf G}}
\def\Gbh{G^{\textrm{BH}}}
\def\Glap{G^{\textrm{L}}}
\def\Ghelm{G^{\textrm{H}}}
\def\Kfark{K^{\textrm{F}}}
\def\II{{\bf I}}
\def\TT{{\bf T}}
\def\bS{{\bf S}}
\def\bD{{\bf D}}
\def\cN{{\mathcal N}}
\def\cK{{\mathcal K}}
\def\cB{{\mathcal B}}
\def\cA{{\mathcal A}}
\def\cS{{\mathcal S}}
\def\cSk{{\mathcal S}_k}
\def\cD{{\mathcal D}}
\def\cDt{{\mathcal D}^{\intercal}}
\def\cDk{{\mathcal D}_{k}}
\def\cDkt{{\mathcal D}_{k}^{\intercal}}
\def\cW{{\mathcal W}}
\def\cJ{{\mathcal J}}
\def\cL{{\mathcal L}}
\def\cA{{\mathcal A}}
\def\cM{{\mathcal M}}
\def\bL{{\mathbb L}}
\def\bK{{\mathbf K}}
\def\sint{{\sin{(n \theta)}}}
\def\cost{{\cos{(n \theta)}}}
\def\jnkr{J_{n}(kr)}
\def\jnk{J_{n}(k)}
\def\jnpkr{J_{n}'(kr)}
\def\jnppkr{J_{n}''(kr)}
\def\jnppk{J_{n}''(k)}
\def\ddr{\frac{d}{dr}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abstract{The boundary integral equation (BIE) framework
  provides robust and scalable eigenvalue computations, which
  owes to the fact that only the boundary of the domain
  must be discretized and that there is no high frequency
  ``pollution'' when using a Green's function to analytically
  represent the propagation of oscillatory waves.
  %
  In this paper, we detail the theoretical justification
  for a BIE approach to the Stokes eigenvalue problem on
  simply and multiply-connected planar domains, which entails
  a treatment of the uniqueness theory for oscillatory
  Stokes equations on exterior domains. 
  %
  Then, using well-established techniques for
  discretizing BIEs and fast linear algebra,
  we present numerical results which confirm
  the analytical claims of the paper and demonstrate
  the efficiency of the overall approach.
}

>>>>

\def\bz{{\boldsymbol 0}}
\def\br{{\boldsymbol r}}
\def\bc{{\boldsymbol c}}
\def\bh{{\boldsymbol h}}
\def\bn{{\boldsymbol n}}
\def\bT{{\boldsymbol T}}
\def\bt{{\boldsymbol t}}
\def\xx{{\boldsymbol x}}
\def\bx{{\boldsymbol x}}
\def\yy{{\boldsymbol y}}
\def\by{{\boldsymbol y}}
\def\ss{{\boldsymbol s}}
\def\tt{{\boldsymbol t}}
\def\uu{{\boldsymbol u}}
\def\bu{{\boldsymbol u}}
\def\be{{\boldsymbol e}}
\def\bl{{\boldsymbol \ell}}
\def\ff{{\boldsymbol f}}
\def\bg{{\boldsymbol g}}
\def\GG{{\bf G}}
\def\Gbh{G^{\textrm{BH}}}
\def\Glap{G^{\textrm{L}}}
\def\Ghelm{G^{\textrm{H}}}
\def\Kfark{K^{\textrm{F}}}
\def\II{{\bf I}}
\def\TT{{\bf T}}
\def\bS{{\bf S}}
\def\bD{{\bf D}}
\def\bC{{\bf C}}
\def\bB{{\bf B}}
\def\cN{{\mathcal N}}
\def\cK{{\mathcal K}}
\def\cB{{\mathcal B}}
\def\cA{{\mathcal A}}
\def\cS{{\mathcal S}}
\def\cSk{{\mathcal S}_k}
\def\cD{{\mathcal D}}
\def\cDt{{\mathcal D}^{\intercal}}
\def\cDk{{\mathcal D}_{k}}
\def\cDkt{{\mathcal D}_{k}^{\intercal}}
\def\cW{{\mathcal W}}
\def\cJ{{\mathcal J}}
\def\cL{{\mathcal L}}
\def\cA{{\mathcal A}}
\def\cM{{\mathcal M}}
\def\bL{{\mathbb L}}
\def\bK{{\mathbf K}}
\def\sint{{\sin{(n \theta)}}}
\def\cost{{\cos{(n \theta)}}}
\def\jnkr{J_{n}(kr)}
\def\jnk{J_{n}(k)}
\def\jnpkr{J_{n}'(kr)}
\def\jnppkr{J_{n}''(kr)}
\def\jnppk{J_{n}''(k)}
\def\ddr{\frac{d}{dr}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\abstract{The boundary integral equation (BIE) framework
  provides robust and scalable eigenvalue computations
  due to (a) the reduction in the dimension of the problem to
  be discretized and (b)
  the absence of high frequency ``pollution'' when using
  a Green's function to represent propagating waves.
  %
  In this paper, we detail the theoretical justification
  for a BIE approach to the Stokes eigenvalue problem on
  simply and multiply-connected planar domains, which entails
  a treatment of the uniqueness theory for oscillatory
  Stokes equations on exterior domains. 
  %
  Then, using well-established techniques for
  discretizing BIEs and fast linear algebra,
  we present numerical results which confirm
  the analytical claims of the paper and demonstrate
  the efficiency of the overall approach.
}
